---
title: "plotGen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{plotGen}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## How to use this package?
This package is made for [Statgarten](https://github.com/statgarten), which is a solution for easy statistical analysis.
This package uses `ggplot()` mainly, and `plot_ly()` as supplementary.
This package returns an interactive ggplot graph, using `ggplotly()`.
There is some plots not supported by `ggplotly()`. For example, in ggplot2, there is no geom function for pie chart or donut chart.
You need to use polar coordination to draw those circular chart. However, `ggplotly()` does not support ploar coordination yet.
This package uses `plot_ly()` to draw plots not supported by `ggplotly()`. You should be careful of it.

Here is a example,

```{r setup}
library(plotGen)
library(ggplot2)
plotGen(mtcars, "scatter", "mpg", "wt", options = c("XScaleToLog10", "YScaleToSqrt", "Theme_BW"), wraptype = "grid", wrapcols = "cyl")
```

You can generate a ggplot2 plot in one line.
